Appendix

### 2014-12-06 Rmarkdown/appendix.Rmd
Minor changes to appendix

```{r dinucleotide_distribution, fig.lp = "fig:dinuclotide_distribution"}
library(ggplot2)
thesis_theme <- theme_classic(base_size = 12)
thesis_theme <- theme_bw(base_size = 12)
edf <- nf %*% t(nf) / (sum(nf %*% t(nf))) * 100
x <- data.frame(Dinucleotide = names(rowSums(df)),
                Observed = as.vector(100 * rowSums(df) / sum(as.numeric(df))),
                Expected = as.vector(edf))
ggplot(x, aes(x = Dinucleotide, y = Observed / Expected)) +
  geom_point(size = 5) + coord_cartesian(ylim = c(0, 1.5)) +
  ggtitle("CpGs are underrepresented in human reference genome (hg19)") +
  thesis_theme +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  geom_hline(yintercept = 1, linetype = 2)
```

@@

```{r cpg_ipds_cdf}
library(ggplot2)
thesis_theme <- theme_classic(base_size = 12)
thesis_theme <- theme_bw(base_size = 12)

@@

### Histogram

```{r cpg_ipds_hist}
library(ggplot2)
library(scales)
thesis_theme <- theme_classic(base_size = 12)
thesis_theme <- theme_bw(base_size = 12)

@@

The computational equivalence of these approaches are shown in the following R code:

>>>>

```{r dinucleotide_distribution, fig.lp = "fig:dinuclotide_distribution", dev = "pdf"}
library(ggplot2)
thesis_theme <- theme_classic(base_size = 12)
thesis_theme <- theme_bw(base_size = 12)
edf <- nf %*% t(nf) / (sum(nf %*% t(nf))) * 100
x <- data.frame(Dinucleotide = names(rowSums(df)),
                Observed = as.vector(100 * rowSums(df) / sum(as.numeric(df))),
                Expected = as.vector(edf))
ggplot(x, aes(x = Dinucleotide, y = Observed / Expected)) +
  geom_point(size = 5) + coord_cartesian(ylim = c(0, 1.5)) +
  ggtitle("CpGs are underrepresented in human reference genome (hg19)") +
  thesis_theme +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  geom_hline(yintercept = 1, linetype = 2)
```

@@

```{r cpg_ipds_cdf, dev = "pdf"}
library(ggplot2)
thesis_theme <- theme_classic(base_size = 12)
thesis_theme <- theme_bw(base_size = 12)

@@

### Frequency polygon

```{r cpg_ipds_hist, dev = "pdf"}
library(ggplot2)
library(scales)
thesis_theme <- theme_classic(base_size = 12)
thesis_theme <- theme_bw(base_size = 12)

@@

The computational equivalence of using Pearson's $\chi^{2}$ test, the deviance of a log-linear model and the deviance of a logistic regression are shown in the following R code:
